### 2018-11-28 Sections/cryptowars.tex
shor
Figure resizing. minor.

\subsection{Public-key cryptography}\index{Public-key cryptography}

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the (strongly held, but unproven) belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{One-way functions}. The algorithm is built upon number theory using modular arithmetic, described in detail in Alg.~\ref{alg:RSA}.

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, changing a single bit in the input string ought to flip approximately half the bits of the hash on average.

>>>>

\subsection{Public-key cryptography}\index{Public-key cryptography}\label{sec:public_key_crypt}

@@

RSA \cite{bib:RSA} was the first published public-key cryptographic protocol, and forms the backbone for most encryption used on the internet today. It achieves its security based on the (strongly held, but unproven) belief that factorising large integers into constituent primes is a computationally hard problem -- a so-called `trapdoor function'\index{One-way functions}. The algorithm is built upon number theory using modular arithmetic. Alg.~\ref{alg:RSA} described the RSA key-generation, encryption, and decryption protocols.

@@

Hash functions have broad applicability throughout computer science, but here we are most interested in \textit{cryptographic hash functions} for use in cryptography, which impose strong conditions on the difficulty of inversion and their quasi-random characteristics. Most notably, the desired characteristics of a cryptographic hash function include:
\begin{itemize}
	\item The distribution of hashes ought not exhibit any biases, following a uniform distribution with quasi-random\index{Quasi-random} behaviour.
	\item Changing a single bit in the input string ought to flip approximately half the bits of the hash on average.	
	\item It's computationally efficient to calculate a hash from an input.
	\item It's computationally complex to find an input that hashes to a given value.
	\item The hashes of two very similar inputs ought to yield hashes that a very different.
	\item Two different inputs are extremely unlikely to hash to the same value.
\end{itemize}

### 2018-11-28 Sections/optimising_the_world.tex
Formatting, algs
Figure resizing. minor.

%Many other algorithms are also known to be \textbf{NP}-complete, a number of which that are relevant to networking are discussed in detail in Sec.~\ref{sec:graph_theory}, summarised in Table.~\ref{tab:net_alg_sum}.

@@

\begin{figure}[!htbp]
\if 3\pubmode
	\includegraphics[clip=true, width=0.8\textwidth]{search_tree}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{search_tree}
\fi
	\captionspacefig \caption{A search tree\index{Search tree}\index{Search-space} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how many moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

@@

Indeed this intuitive example is a very powerful one -- since all \textbf{EXP}-complete problems are by definition equivalent, and \textbf{EXP} contains many other lesser (but hard) classes, the approximate optimisation technique immediately captures a vast array of interesting problems.

>>>>

%Many other algorithms are also known to be \textbf{NP}-complete, a number of which that are relevant to networking are discussed in detail in Sec.~\ref{sec:graph_theory}, summarised in Tab.~\ref{tab:net_alg_sum}.

@@

%\if 3\pubmode
\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.7\textwidth]{search_tree}
%\else
%	\includegraphics[clip=true, width=0.475\textwidth]{search_tree}
%\fi
	\captionspacefig \caption{A search tree\index{Search tree}\index{Search-space} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e its distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, \mbox{$|V|=O(\exp(d))$}, the configuration search space in a game grows exponentially with how many moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\if 3\pubmode
\end{figure*}
\else
\end{figure*}
\fi

@@

Indeed this intuitive example is a very powerful one -- since all \textbf{EXP}-complete problems are by definition equivalent, and \textbf{EXP} contains many other lesser (but nonetheless hard) classes, the approximate optimisation technique immediately captures a vast array of interesting problems.

### 2018-11-28 Sections/the_quantum_space_race.tex
Fixed up fig sizes for 1 col
Figure resizing. minor.

In general, the distance to the horizon $d$ (in kilometres)\index{Distance to horizon} on the Earth's surface at an altitude of $h$\index{Ground stations!Aharltitude} (in metres) is given by the approximation,
\begin{align}
d \approx 3.57\sqrt{h}.
\end{align}
This relationship is shown in Fig.~\ref{fig:dist_hor}, covering the range of altitudes from sea level\index{Sea level} to the summit of Mount Everest (8,848m)\index{Mount Everest}. It is evident that line-of-sight\index{Line-of-sight} channels across the Earth's surface are inherently limited by the curvature of the Earth to $\sim$250km, using altitudes that are practically realistic (i.e no ground stations on the summit of Everest thank you very much!).

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{distance_to_horizon}
\captionspacefig \caption{Distance to the horizon $d$ (in kilometres), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realistic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic, and only achievable in some parts of the globe), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}

>>>>

In general, the distance to the horizon $d$ (in kilometres)\index{Distance to horizon} on the Earth's surface at an altitude of $h$\index{Ground stations!Altitude} (in metres) is given by the approximation,
\begin{align}
d \approx 3.57\sqrt{h}.
\end{align}
This relationship is shown in Fig.~\ref{fig:dist_hor}, covering the range of altitudes from sea level\index{Sea level} to the summit of Mount Everest (8,848m)\index{Mount Everest}. It is evident that line-of-sight\index{Line-of-sight} channels across the Earth's surface are inherently limited by the curvature of the Earth to $\sim$250km, using altitudes that are practically realistic (i.e no ground stations on the summit of Everest thank you very much!).

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{distance_to_horizon}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{distance_to_horizon}
\fi
\captionspacefig \caption{Distance to the horizon $d$ (in kilometres), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realistic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic, and only achievable in some parts of the globe), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}
